Scaffolder - Software for \change{Reproducible}{Manual} Genome Scaffolding.

### 2011-08-15 src/article.tex
Revise discussion

Scaffolding an incomplete genome assembly requires joining contigs and
additional gap-filling sequence\add{s} using a combination of computational and
laboratory methods. The process of manually editing a scaffold is inherently
hard to reproduce and introduces \remove{the possibility of }irreducible
\change{techniques}{edits} and/or human error. In respect to \change{these
drawbacks}{this} the aims of the Scaffolder software are twofold: 1) to provide
software that is easy to install and simplifies the task of genome finishing;
and 2) to facilitate reproducibility in the scaffolding and finishing stage of
a genome project. \pb

\subsection*{Comparison with other scaffold formats} %{{{2

@@

\add{AGP is a similar format for describing scaffolds. This format can be used
to define contig order and N-filled gap regions in a scaffold. The advantages
of the AGP format is that each contig entry is defined on a single line which
allows searching the scaffold using UNIX line-based tools. The scaffolder
format in comparison in contrast is written in the standardised YAML format
and therefore accessible to the many languages which provide parsers to this
format. The scaffolder format is provided with a tool explicitly to produce
the fasta sequence of scaffold specified by in the file.} \pb

@@

\subsection*{Example Use Case} %{{{2

\add{The example use case for scaffolder is a combination of computation and
manual editing of a genome scaffold. We have used scaffolder in our genome
projects to create a scaffold file from parsing the output of \emph{in silico}
scaffolding tools into the scaffold file format. This scaffold was then
manually updated in a text editor to fill gap regions with laboratory-produced
sequences.} \pb

>>>>

Scaffolding an incomplete genome assembly requires joining contigs and
additional gap-filling sequence\add{s} using a combination of computational and
laboratory methods. The process of manually editing a scaffold is inherently
hard to reproduce and introduces \change{the possibility of irreducible of
techniques}{irreproducible edits} and/or human error. In respect to
\change{these drawbacks}{this} the aims of the Scaffolder software are
twofold: 1) to provide software that is easy to install and simplifies the
task of genome finishing; and 2) to facilitate reproducibility in the
scaffolding and finishing stage of a genome project. \pb

@@

\add{AGP is a similar format for describing scaffolds. This format can be used
to describe contig order and N-filled gap regions in a scaffold. The
advantages of the AGP format is that each contig entry is defined on a single
line which allows searching the scaffold using UNIX line-based tools. The
scaffolder format in comparison in contrast is written in the standardised
YAML format and therefore accessible to the many languages which provide
parsers to this format. The scaffolder format is provided with a tool
explicitly to produce the fasta sequence of scaffold specified by in the file.
The scaffold format further provides functions for trimming and replacing
regions of sequence using inserts.} \pb

@@

\add{An example use case for scaffolder is a combination of computational and
manual editing of a genome scaffold. We have used scaffolder in our own genome
projects to create an initial scaffold from compuationally parsing the output
of \emph{in silico} scaffolding tools into YAML. This scaffold was then
manually updated as the scaffold was finished with additional gap-filling
sequences generated in the laboratory.} \pb
